Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
text2

\subsubsection{Effect on safety specification and stability}
%Thus we can consider the effect of these errors on our safety and stability verification.

First consider the effect of the quantization errors on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.

The inputs are computed using the following equations. 
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
\end{align*}

This will induce two types of the error detailed above, first the truncation errors due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$, and second the rounding error introduced by the multiplication. We represent these errors as non-deterministic noise.

A further error is caused by the representation of the plant dynamics.
\begin{align*}
x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{align*}

We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.

We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details). 
In this paper, we require stability ony as a precusros to safety and it is therefore sufficient that the system converges to a point within the safe states. Hence, it is sufficient to disregard these errors when we synthesize a stable controller, and then verify safety.

>>>>

\subsubsection{Effect on safety specification and stability}

Let us first consider the effect of the quantization errors on safety. 
Within the digital controller block, 
state values are manipulated at low digital precision, 
alongside the vector multiplication $Kx$.   
%computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
As such, the inputs are computed using the following equation: 
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
\end{align*}

This induces two types of the errors detailed above:  
first, the truncation error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$; 
and second, the rounding error introduced by the multiplication operation. 
We represent these errors as non-deterministic noise.

An additional error is caused by the representation of the plant dynamics, namely 
\begin{align*}
x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{align*}

\todo{You mean the second one, or both? Please clarify.} We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.

We note that the effect on stability due to the fixed-word-length error is that the system may, 
instead of converging to the desired equilibrium point, 
converge to a neighbourhood around the desired equilibrium point (see Appendix for details). 
However, since In this paper we require stability only as a precursor to safety, 
it is sufficient to check the (perturbed, noisy) model converges to a point within the safe states. 
In the following, we shall disregard these errors when we synthesise a stable controller, 
and then verify its safety accounting for the finite-precision errors.
